### 2025-02-27 paper/conclusions.tex
Address some comments.

>>>>

The asymptotic efficiency of our AD implementation depends crucially
on ``ad-hoc'' optimisations of summations of arrays with only a single
nonzero element. Although effective in many cases, this can be seen as
a somewhat fragile technique, and will likely not work for a richer
language with more complicated control flow, but this limitation is
not fundamental to our approach: in the future, we could for example
use an sparse representation of adjoint arrays instead.
